Trends of SDR in Thessaloniki

### 2023-09-18 Article.Rmd
Commit 2023-09-18 18:14

```{r szatrends, echo = FALSE, fig.cap='Distribution of the SDR\'s long term trends by SZA before and after noon. The solid data points represent values with an acceptable statistical significance ($p<0.005$).', fig.subcap=c('All-sky conditions.', 'Clear-sky conditions.', 'Cloud-sky conditions.'), out.width='.35\\linewidth', out.width='.32\\linewidth', fig.asp=1, fig.ncol = 3}
knitr::include_graphics("./images/SzaTrends-13.png")
knitr::include_graphics("./images/SzaTrends-17.png" )
knitr::include_graphics("./images/SzaTrends-21.png")
```

@@

<!-- \footnotesize -->
```{r trendseasontable, echo=F}

## arrange columns
spp <- spp[,c(
      "Sky condition",
      "Season",
      "Trend [%/year]", 
      # "Trend p-value", 
      "Statistical signif. [%]"
      )]

rownames(spp) <- NULL
# panderOptions("table.alignment.default", "left")
panderOptions("table.alignment.default", "center")
pander(spp,
       justify = c('center', 'right', 'right', 'right', 'center'),
       split.table = Inf,
       caption = "\\label{tab:trendseasontable}SDR linear trends of monthly anomalies for each season of the year.")
```
<!-- \normalsize -->

@@

```{r  echo=F, fig.cap="Seasonal SZA"}
knitr::include_graphics("./images/SzaTrendsSeas-1.png")
```

```{r  echo=F, fig.cap="Seasonal SZA"}
knitr::include_graphics("./images/SzaTrendsSeas-2.png")
```

```{r  echo=F, fig.cap="Seasonal SZA"}
knitr::include_graphics("./images/SzaTrendsSeas-3.png")
```

```{r  echo=F, fig.cap="Seasonal SZA"}
knitr::include_graphics("./images/SzaTrendsSeas-4.png")
```

```{r  echo=F, fig.cap="Seasonal SZA"}
knitr::include_graphics("./images/SzaTrendsSeas-5.png")
```

```{r  echo=F, fig.cap="Seasonal SZA"}
knitr::include_graphics("./images/SzaTrendsSeas-6.png")
```

```{r  echo=F, fig.cap="Seasonal SZA"}
knitr::include_graphics("./images/SzaTrendsSeas-7.png")
```

```{r  echo=F, fig.cap="Seasonal SZA"}
knitr::include_graphics("./images/SzaTrendsSeas-8.png")
```

```{r  echo=F, fig.cap="Seasonal SZA"}
knitr::include_graphics("./images/SzaTrendsSeas-9.png")
```

```{r  echo=F, fig.cap="Seasonal SZA"}
knitr::include_graphics("./images/SzaTrendsSeas-10.png")
```

```{r  echo=F, fig.cap="Seasonal SZA"}
knitr::include_graphics("./images/SzaTrendsSeas-11.png")
```

```{r  echo=F, fig.cap="Seasonal SZA"}
knitr::include_graphics("./images/SzaTrendsSeas-12.png")
```

>>>>

```{r szatrends, echo = FALSE, fig.cap='Distribution of the SDR\'s long term trends by SZA before and after noon. The solid data points represent values with an acceptable statistical significance ($p<0.005$).', fig.subcap=c('All-sky conditions.', 'Clear-sky conditions.', 'Cloud-sky conditions.'), out.width='.32\\linewidth', fig.asp=1, fig.ncol = 3}
knitr::include_graphics("./images/SzaTrends-13.png")
knitr::include_graphics("./images/SzaTrends-17.png" )
knitr::include_graphics("./images/SzaTrends-21.png")
```

@@

<!-- \footnotesize -->
```{r trendseasontable, echo=F}
## arrange columns
spp <- spp[,c(
      "Sky condition",
      "Season",
      "Trend [%/year]", 
      # "Trend p-value", 
      "Statistical signif. [%]"
      )]

rownames(spp) <- NULL
# panderOptions("table.alignment.default", "left")
panderOptions("table.alignment.default", "center")
pander(spp,
       justify = c('center', 'right', 'right', 'center'),
       split.table = Inf,
       caption = "\\label{tab:trendseasontable}SDR linear trends of monthly anomalies for each season of the year.")
```
<!-- \normalsize -->

@@

```{r  echo=F, fig.cap="Seasonal SZA", out.width='.32\\linewidth'}
knitr::include_graphics("./images/SzaTrendsSeas-1.png")
```

```{r  echo=F, fig.cap="Seasonal SZA", out.width='.32\\linewidth'}
knitr::include_graphics("./images/SzaTrendsSeas-2.png")
```

```{r  echo=F, fig.cap="Seasonal SZA", out.width='.32\\linewidth'}
knitr::include_graphics("./images/SzaTrendsSeas-3.png")
```

```{r  echo=F, fig.cap="Seasonal SZA", out.width='.32\\linewidth'}
knitr::include_graphics("./images/SzaTrendsSeas-4.png")
```

```{r  echo=F, fig.cap="Seasonal SZA", out.width='.32\\linewidth'}
knitr::include_graphics("./images/SzaTrendsSeas-5.png")
```

```{r  echo=F, fig.cap="Seasonal SZA", out.width='.32\\linewidth'}
knitr::include_graphics("./images/SzaTrendsSeas-6.png")
```

```{r  echo=F, fig.cap="Seasonal SZA", out.width='.32\\linewidth'}
knitr::include_graphics("./images/SzaTrendsSeas-7.png")
```

```{r  echo=F, fig.cap="Seasonal SZA", out.width='.32\\linewidth'}
knitr::include_graphics("./images/SzaTrendsSeas-8.png")
```

```{r  echo=F, fig.cap="Seasonal SZA", out.width='.32\\linewidth'}
knitr::include_graphics("./images/SzaTrendsSeas-9.png")
```

```{r  echo=F, fig.cap="Seasonal SZA", out.width='.32\\linewidth'}
knitr::include_graphics("./images/SzaTrendsSeas-10.png")
```

```{r  echo=F, fig.cap="Seasonal SZA", out.width='.32\\linewidth'}
knitr::include_graphics("./images/SzaTrendsSeas-11.png")
```

```{r  echo=F, fig.cap="Seasonal SZA", out.width='.32\\linewidth'}
knitr::include_graphics("./images/SzaTrendsSeas-12.png")
```
